\documentclass[12pt]{turabian-researchpaper}

\usepackage[utf8]{inputenc}
\usepackage{csquotes,ellipsis,xurl}
\usepackage[pass, letterpaper]{geometry}
\usepackage{biblatex-chicago}

\newcommand\question[2]{\noindent\textbf{#1: #2}}

\title{Week 6}
\subtitle{Response Paper}
\author{Eric Altenburg}
\course{HST 415: The Nuclear Era}
\date{\today}

\raggedright

\begin{document}
	\maketitle

	\question{1}{Questions about this that came to mind during lecture or the readings — at least one good one!}

		\begin{itemize}
			\item In the lecture video, how do you think the idea of secrecy has changed with today's standards in regard to electronic documents and emails? More or less secure than the Manhattan Project days?
			\item For the Rosenberg trial protests, were the people protesting mainly aligned with the Communist party or did they just feel the trial was unjust?
			\item \textit{Said in the same voice from lecture} \newline
				How did you find the original Oppenheimer hearings Professor Wellerstein?
		\end{itemize}

	\question{2}{What does the JCAE hearing above, and the Oppenheimer security clearance hearing, reveal about what the JCAE and AEC were afraid of with regards to personnel security clearances? What kinds of things seem to matter the most to them? What does this tell us about their time?}


	\question{3}{What does the case of the Rosenbergs and VENONA (discussed in the lecture) tell us about the attitudes towards secrecy and the atomic bomb in the US in the 1950s?}


	\question{4}{For the case from the DOE website (a present-day approach) — if you took it as representative of OUR current attitudes towards personnel security clearances, what seems to matter the most? In comparing it with the JCAE and Oppenheimer cases, what does it reveal about the changes that have happened from the 1940s-1950s and the present-day?}


	\question{5}{Lastly — with regards to Oppenheimer, what is your ultimate verdict? If you had been on the board making the judgment about Oppenheimer, how would you have ruled?}

\vspace*{\fill}
\noindent\textit{I pledge my honor that I have abided by the Stevens Honor System.} -Eric Altenburg

\end{document}